The Globular Cluster System of the Auriga Simulations

### 2019-03-26 AurigaGCS.tex
Mass-weighted Rgc-FeH plot of MW and M31 without scattering the observed points

\todo[inline]{
TODO: paraphrase ``The diversity in morphological properties of these simulated 
galaxies reflects the stochasticity inherent to the process of galaxy formation 
and evolution 
\citep[e.g.][]{2005ApJ...635..931B, 2010MNRAS.406..744C, 2010ApJ...708.1398T}.''
}

\todo[inline]{Paragraph about Auriga's stellar haloes.
``The Auriga Stellar Haloes: Connecting stellar population properties with
accretion and merging history'' \citet{2018arXiv180407798M}
}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]
        {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
    \includegraphics[width=\columnwidth]
        {{M31_RgcFeH_HistogramMassWeighted_CaldwellRomanowsky2016data}.png}
    \caption{
        \emph{Top}: Mass-weighted r$_{\text{gc}}$-[Fe/H] distribution of
        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
        is 98.19 \% of the total MW GCS mass in the Harris catalog.
        \emph{Bottom}: Same for M31, showing 366 GCs and 88.38 \% of the total 
        mass in CR16 \citep[data from][]{2016ApJ...824...42C}.
        \label{fig:MW-FeHRgc}
    }
\end{figure}

@@

\subsection{Metallicity distribution}
\label{sec:metallicity}
We investigate whether the star formation model implemented in the Auriga 
simulations is capable of i) producing a metallicity distribution that is 
consistent with the GCS observed in the MW (M31), and ii) generating sufficient 
mass over the full domain of the observations.

In Figure~\ref{fig:FeH} we show a mass-weighted metallicity 
distribution where the lines show the median value of all thirty Auriga level 4 
haloes for \emph{all stars} (orange dotted), \emph{old stars / GC candidates} 
(orange solid), \emph{old in-situ} stars (blue solid), and \emph{old accreted} stars
(red solid). The shaded regions indicate the $1\sigma$ interval around the median 
(i.e. the scatter between runs with different initial conditions and merger
histories). The MW (M31) GCS is shown in purple (magenta). We use the 
same bin sizes for the simulations as for the observations, explicitly shown for
the observed profiles.

@@

>>>>

The Auriga suite has a fiducial resolution level L4, accompanied by the lower 
(higher) level L5 (L3) that is available for selected initial condition runs.
The baryonic mass resolution in order of increasing level is $m_b$~=~[$4 \times 10^5$,
$5 \times 10^4$, $6 \times 10^3$]~M\Sun \, with gravitational softening of 
collissionless particles $\epsilon$~=~[$738, 369, 184$]~pc.

% \todo[inline]{
% TODO: paraphrase ``The diversity in morphological properties of these simulated 
% galaxies reflects the stochasticity inherent to the process of galaxy formation 
% and evolution 
% \citep[e.g.][]{2005ApJ...635..931B, 2010MNRAS.406..744C, 2010ApJ...708.1398T}.''
% }
% 
% \todo[inline]{Paragraph about Auriga's stellar haloes.
% ``The Auriga Stellar Haloes: Connecting stellar population properties with
% accretion and merging history'' \citet{2018arXiv180407798M}
% }

@@

\begin{figure}
    \includegraphics[width=\columnwidth]
        {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
    \includegraphics[width=\columnwidth]
        {{M31_RgcFeH_HistogramMassWeighted_CaldwellRomanowsky2016data}.png}
    \caption{
        \emph{Top}: Mass-weighted R$_{\text{GC}}$-[Fe/H] distribution of
        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
        is 98.19 \% of the total MW GCS mass in the Harris catalog.
        \emph{Bottom}: Same for M31, showing 366 GCs and 88.38 \% of the total 
        mass in CR16 \citep[data from][]{2016ApJ...824...42C}. Note that the
        range of the colourmap differs in both figures.
        \label{fig:MW-FeHRgc}
    }
\end{figure}

@@

\subsection{Metallicity distribution}
\label{sec:metallicity}
We investigate whether the star formation model implemented in the Auriga 
simulations is capable of i) producing a metallicity distribution that is 
consistent with the GCS observed in the MW (M31), and ii) generating sufficient 
mass over the domain of the observations.

@@

Figure~\ref{fig:FeH} shows a mass-weighted metallicity distribution of the
Auriga L4 median
for \emph{all stars} (orange dotted), \emph{old stars / GC candidates} 
(orange solid), \emph{old in-situ} stars (blue solid), and \emph{old accreted} stars
(red solid). The shaded regions indicate the $1\sigma$ interval around the median 
(i.e. the scatter between runs with different initial conditions and merger
histories). The MW (M31) GCS is shown in purple (magenta). We use the 
same bin sizes for the simulations as for the observations, explicitly shown for
the observed profiles.
